---
title: "Storing and Accessing Secrets in Azure Key Vault"
execute:
  eval: false
categories:
  - Slack
authors: Miel Hostens, Enhong Liu et al.
date: 07/25/25
toc: true
---

Before accessing the secret in Databricks, make sure to:

1. ✅ Talk to **Enhong** or **Miel** to store the key in the Azure Key Vault.
2. ✅ Use the secret scope `bovi_analytics_secrets_scope` in Databricks.
3. ✅ Use personal compute instead of serverless.
---

## 🔐 Access the Key in Databricks

Use the following code snippet to retrieve the secret:

```{r}
#| eval: false
#| include: true
# Retrieve secret from Azure Key Vault via Databricks Secret Scope
    # Replace <data> with the actual data name you want to access
    # Replace <your-key-name> with the actual key name you want to access.
<data>_secret = dbutils.secrets.get(scope="bovi_analytics_secrets_scope", key= <your-key-name> )

# Print the secret (only for debugging; avoid in production)
print(<data>_secret)
```

## Overview of blob storage accounts and keys

| blob-storage-account | scope                        | key                                  |
|----------------------|------------------------------|--------------------------------------|
| lab-us               | bovi_analytics_secrets_scope | azure-bovi-analytics-lab-us          |
| lab-eu               | bovi_analytics_secrets_scope | azure-bovi-analytics-lab-eu          |
| gpluse               | bovi_analytics_secrets_scope | azure-bovi-analytics-gpluse-eu       |
| playbehavior         | bovi_analytics_secrets_scope | azure-bovi-analytics-playbehavior-eu |
| methanedata          | bovi_analytics_secrets_scope | azure-bovi-analytics-methanedata-us  |

azure-bovi-analytics-methanedata-us

## Real Example: Accessing Bovi-Analytics Data from Azure Blob Storage

In this example, we use a secret stored in Azure Key Vault (retrieved via Databricks Secret Scope) to authenticate and access data stored in an Azure Blob Storage account.

```{r}
#| eval: false
#| include: true
%scala
// Set the Azure Blob Storage account key using the Databricks secret
spark.sparkContext.hadoopConfiguration.set(
   "fs.azure.account.key.blob-storage-account.blob.core.windows.net",
   dbutils.secrets.get(scope="bovi_analytics_secrets_scope", key= "key")
   )
```

```{r}
#| eval: false
#| include: true
%python
// Set the Azure Blob Storage account key using the Databricks secret
spark.conf.set(
   "fs.azure.account.key.blob-storage-account.blob.core.windows.net",
   dbutils.secrets.get(scope="bovi_analytics_secrets_scope", key= "key")
   )
```

```{r}
#| eval: false
#| include: true
# Accessing farm data stored in blob storage
file_location = "wasbs://container-name@blob-storage-acount.blob.core.windows.net/path-to-file/"
file_type = "txt"
data_set = spark.read.format(file_type).load(file_location)
display(data_set)
```

